---
title: "Reproducible Research"
output: github_document
---

reproducable research
======================
영어로 작성하는 이유는 영어공부를 하기 위함이다

### slide1. coding standard in R
1. easy to convert
- basic text format is easy to use any environment, convert any format and editor
- ASCII encoding is standard in english culture
- R studio saves files as text format

2. easy to read
- indenting is improtant to make readable code, recommend tab space is 8
- limit code width as 80 column
- simple function is better to read and trace bug


### slide2. markdown

putting double space at the end of line equal to new line  
*ltalic*  
**Bold**  
# h1  
## h2  
### h3  
#### h4  
##### h5  
- unordered list, list formats dose not need double space
1. ordered list, actualy it just character
1. but if you inpur number like this, it convert character to ordered list
1. as you see. number 1 change to 2,3

[link has 2 way](https://www.coursera.org/learn/reproducible-research/lecture/7TTqT/markdown/)
If you feel 1st solution is dirty you can do [this][1] , and use double space  
[1]: https://www.coursera.org/learn/reproducible-research/lecture/7TTqT/markdown "this"

http://github.com - automatic!
[GitHub](http://github.com)

출처는 [위키백과][wiki]입니다.
[wiki]: http://en.wikipedia.org/wiki/Markdown#Syntax_examples "위키백과 Markdown 항목"

# markdown idea is based on simplify markup languege use
# 마크다운은 여러 형태로 쉽게 변환 될 수 있는데, HTML은 그 중 하나일 뿐이다
R markdown 은 마크다운과 같은 형식을 가지지만, R 코드가 그 안에 결합된 것 뿐

knitr package convert R code to basic markdown
markdown package convert markdown to HMTL
use slidfy package can make HTML slide like coursera




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


