---
title: "Reproducible Research"
output: github_document
---

reproducable research
======================

### coding standard in R
1. easy to convert
- basic text format is easy to use any environment and convert any format, editor
- ASCII encoding is standard in english culture
- R studio saves files as text format

2. easy to read
- indenting is improtant to make readable code, recommend tab space is 8
- limit code width as 80 column
- simple function is better to read and trace bug



# markdown idea is based on simplify markup languege use
# 마크다운은 여러 형태로 쉽게 변환 될 수 있는데, HTML은 그 중 하나일 뿐이다
R markdown 은 마크다운과 같은 형식을 가지지만, R 코드가 그 안에 결합된 것 뿐

knitr package convert R code to basic markdown
markdown package convert markdown to HMTL
use slidfy package can make HTML slide like coursera




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


