---
title: "Reproducible Research"
output: github_document
---

영어로 작성하는 이유는 성민이가 보고, 어색한 문장을 알려주면 영어공부가 될 꺼 같아서임 :)

### slide1. coding standard in R

1. easy to convert
- basic text format is easy to use any environment, convert any format and editor
- ASCII encoding is standard in english culture
- R studio saves files as text format

2. easy to read
- indenting is improtant to make readable code, recommend tab space is 8
- limit code width as 80 column
- simple function is better to read and trace bug


### slide2. markdown syntax

title
======================

putting double space at the end of line equal to new line  

you can also use br/ tag to make new line<br/>
*ltalic*  

**Bold**  

# h1  
## h2  
### h3  
#### h4  
##### h5  

- unordered list, list formats dose not need double space
1. ordered list, actualy it just character
3. but if you inpur number like this, it convert character to ordered list
2. as you see in the code, any number autometically changes sequently

[link has 2 way](https://www.coursera.org/learn/reproducible-research/lecture/7TTqT/markdown/)
If you feel 1st solution is dirty you can do [this][1]  

[1]: https://www.coursera.org/learn/reproducible-research/lecture/7TTqT/markdown "this"  

#### the weired thing  

> 1st. some functions does not work in github document such as new line(doble space), link.<br/>
> If this happens, put one empty line after new line<br/>
> 2nd. every list format number is changes ordered list, so it is hard to start more than 1


### slide3. R markdown
1. what is Rmd?
- markdown can convert several format, HTML is one of them
- Rmd (R markdown) is enbeding R code and markdown

2. work process of Rmd
- knitr package convert R code to basic markdown
- markdown package convert markdown to HMTL
- use other packages can make other function like slidfy package?


### slide4. R markdown demonstration
1. R code
```{r}
# you can see the R code that I wrote, and Console outputs
library(datasets)
summary(airquality)
```

you can add settings in {r}

```{r pressure, echo=FALSE}
plot(pressure)
```

#### for reading oter platform like web, github
- need to convert .Rmd to .md in the Rstudio using knit function
- need to upload every output such as graph, img
- If some of R code make error than all R code do not make result


### slide5. literate statistical programming with knitr (part1)

1. what is literate statistical programming?
- [literate programming][1] is a method to make code readable to both human and machine when programming
- make one code file mixed with documentation and programming language
- knitr support a variety of documentation languages
[1]: https://ko.wikipedia.org/wiki/%EB%AC%B8%ED%95%99%EC%A0%81_%ED%94%84%EB%A1%9C%EA%B7%B8%EB%9E%98%EB%B0%8D "한국어 설명"

2. how to make work reproducible?
- do literate programming at the begining of the project
- keep track data manupulation so you can know how you got there
- do not save output such as temp data. raw data + preprocessing code is better than clean data set
- save data in non-proprietary formats

3. pros

4. cons
